Discrete Quantum Theories and Computing

### 2019-02-21 dissertation.tex
dissertation.lyx Secs. 4.4, 4.5, and 4.6 Reviewed...

\begin{table}[!t]
\begin{doublespace}
\noindent \centering{}\caption{\label{tab:teacher}Other courses I took which is relevant to this
dissertation, where IUB stands for Indiana University Bloomington
and NTU stands for National Taiwan University.}
%% ERT block 1 (before LyX tabular)
\renewcommand{\tabular}{\tabularx{\linewidth}}
\renewcommand{\endtabular}{\endtabularx} 
\begin{tabular}{M{Chou~(周謀鴻)}cM{MATH-M522}Y}
\toprule 
Instructor & School & Course & Relation with the dissertation\tabularnewline
\midrule
\midrule 
Tom Lewis & IUB & SLST-T501 & Sec.~\ref{subsec:Discrete-Deutsch-algorithm} is based on the term
paper of \emph{Academic Writing}.\tabularnewline
\midrule 
Michael\nolinebreak[3] A. Mandell & IUB & MATH-M522 & The textbook~\cite{Hatcher2001} of \emph{Topology II} is cited
in Chapters~\ref{chap:Introduction} and~\ref{chap:Conventional-Quantum-Theory}.\tabularnewline
\midrule 
Steven Myers & IUB & CSCI-B502 & The textbook~\cite{AroraBarak2009} of \emph{Computational Complexity}
is cited in Sec.~\ref{modalquantumcomputing}.\tabularnewline
\midrule 
Valery Lunts & IUB & MATH-M501 & The textbook~\cite{DummitFoote2004} of \emph{Survey of Algebra}
is cited in Secs.~\ref{sec:background}, \ref{discretequantumtheoryI},
and~\ref{discretequantumtheoryIIb}.\tabularnewline
\midrule 
Huah Chu\linebreak[3] (朱樺\textenglish[variant=american]{)} & NTU & 221~U3830\linebreak[3] 221~U3840 & The textbook~\cite{Artin1991} of \emph{Algebra (I)} and \emph{(II)}
is cited in Secs.~\ref{subsec:Two-dimensional-Hilbert-Space}, \ref{subsec:Cyclic-Properties-of},
\ref{subsec:Complexified-Finite-Fields}, and~\ref{discretequantumtheoryIIb}.\tabularnewline
\midrule 
Jin-Tzu Chen\linebreak[3] (陳金次) & NTU & 201~31300 & The textbook~\cite{GAMELIN2003} of \emph{Functions of a Complex Variable}
is cited in Sec.~\ref{subsec:Vector-Spaces}.\tabularnewline
\midrule
Mo-Hong\linebreak[3] Chou (周謀鴻) & NTU & 221~U4290 & The textbook~\cite{GolubVanLoan1996} of \emph{Introduction to Computational Linear Algebra}
is cited in Sec.~\ref{subsec:Finite-Precision-Extension-of}.\tabularnewline
\bottomrule
\end{tabular}% ERT block 2 (after LyX tabular)
\renewcommand{\tabular}{\ORIGtabular}
\renewcommand{\endtabular}{\ORIGendtabular} 
\end{doublespace}
\end{table}
Many people have done everything to make my double-major smooth. I
need to thank all of their supports, financially or providing some
experience, as listed in my Curriculum Vitae at the end of the dissertation.
Most importantly, Prof.\ Amr A. Sabry\ (\textarabic{عمرو صبري})
helped me deal with the rules, supervised my reading courses for writing
our papers, and financially support me as a research assistant and
associate. In the department of Mathematics, I need to thank the graduate
services assistant, Kate Forrest, and the directors of graduate study
in Mathematics, especially Prof.\ Christopher Judge, Prof.\ Matthias
Weber, and Prof.\ Michael A.\ Mandell. In the department of Computer
Science, I want to thank the graduate student office; the director
of AI/UI assignments, Charles Pope; the directors of \PhD study in
Computer Science, especially Prof.\ Yuqing Melanie Wu (吴愈青) and Prof.\ \textturkish{Funda
Ergun}; and the infrastructure and technology group (ITG). Particularly,
I don't know how much computational power I consumed to count the
states in Sec.~\ref{subsec:Maximal-entanglement}. This computational
power not only came from the Linux systems in Computer Science but
also came from the Big Red II administrated by University Information
Technology Services (UITS). Indiana University Libraries was also
extremely helpful during my dissertation research. Except for a stack
of books I checked out directly, while the books are not in their
collection, I occasionally requested them via the Interlibrary Loan
service or recommended IU libraries to purchase them.

@@

\begin{table}
\begin{doublespace}
\noindent \centering{}\caption{\label{tab:Possible-f}All Possible $f\colon\boolt\rightarrow\boolt$.}
\begin{tabular}{ccccc}
\toprule 
$x$ & $f_{1}\left(x\right)$ & $f_{2}\left(x\right)$ & $f_{3}\left(x\right)$ & $f_{4}\left(x\right)$\tabularnewline
\midrule
$\bfalse$ & $\bfalse$ & $\bfalse$ & $\btrue$ & $\btrue$\tabularnewline
$\btrue$ & $\bfalse$ & $\btrue$ & $\bfalse$ & $\btrue$\tabularnewline
\midrule 
constant or balanced? & constant & balanced & balanced & constant\tabularnewline
\bottomrule
\end{tabular}
\end{doublespace}
\end{table}
\begin{comment}
\todo{We typeset $U_{f}$ either directly or use macro \textbackslash uf,
but the definition of \textbackslash uf has a negative space between
$U$ and $f$ which is different from U\_\{f\}\ldots{} I need to understand
whether the negative space is necessary or not, or whether the negative
space has any semantic meaning\ldots{} }
\end{comment}
\begin{figure}[!b]
\noindent \centering{}
\[
\begin{array}{c}
\xyR{.9em}\xyC{.6em}\entrymodifiers={@*=<0em>}\xymatrix{ & \ar@{.}[ddd] &  & \ar@{.}[ddd] &  & \ar@{.}[ddd] &  & \ar@{.}[ddd]\\
\lstick{\ket{1}} & \qw & \gate{H} & \qw & \multigate{1}{\uf} & \qw & \gate{H^{\dagger}} & \qw & \multimeasureD{1}{\text{measure}}\\
\lstick{\ket{0}} & \qw & \gate{H} & \qw & \ghost{\uf} & \qw & \gate{H^{\dagger}} & \qw & \ghost{\text{measure}}\\
 & \push{\ket{\Phi_{1}}} &  & \push{\ket{\Phi_{2}}} &  & \push{\ket{\Phi_{3}}} &  & \push{\ket{\Phi_{4}}}
}
\end{array}
\]
\caption{\label{fig:Quantum-Circuit-Deutsch}Quantum Circuit for the Deutsch
Algorithm.}
\end{figure}
Although having no realistic application, the Deutsch algorithm is
the first quantum algorithm which outperforms any possible classical
algorithm for the Deutsch problem \cite{Deutsch1985,544199,Mermin2007}.
The Deutsch problem is to decide whether a function $f\colon\boolt\rightarrow\boolt$
is constant or balanced. As listed in Table~\ref{tab:Possible-f},
we have only $4$ different $f$: $2$ of them are constant while
another $2$ are balanced. Similar to our $\usat$ algorithm in Sec.~\ref{modalquantumcomputing},
we start by representing $f$ as a Deutsch black box $U_{f}$ in the
middle of the quantum circuit, Figure~\ref{fig:Quantum-Circuit-Deutsch}.
To explain why this circuit solves the Deutsch problem, we then compute
the state in each step explicitly and express them in the Dirac bracket
notation and its matrix representation in the computational basis
$\left\{ \ket{00},\ket{01},\ket{10},\ket{11}\right\} $.

@@

As an example, consider the field $\ff{23}$. Looking at the squares
of the numbers $\ff{23}=\{0,\ldots,22\}$ modulo 23, we find the $2$-centered
uninterrupted sequence $S_{2}\left(5\right)=\left\{ 0,1,2,3,4\right\} $,
followed by $5$, which is both the smallest quadratic non-residue
and the size of the uninterrupted sequence of quadratic residues (including
$0$) of interest. In particular, it is possible to construct a total
order for the elements $S_{0}\left(5\right)=\left\{ -2,-1,0,1,2\right\} $
in the fields $\ff{23}$, $\ff{71}$, $\ff{311}$, etc., but not in
the smaller fields $\ff{3}$ and $\ff{7}$.

@@

Although division is not an allowed operation for the elements in
an ordered region, following the standard procedure to define a conventional
fraction as a pair of integers \cite{Artin1991,DummitFoote2004,hottbook2013,Wolfram2016},
we could define a \emph{cardinal probability} as a pair of order-region
elements as well:
\begin{equation}
\muC_{\Psi}\left(i\right)=\cardp{\fnorm{\ip{i}{\Psi}}}{\fnorm{\ket{\Psi}}}=\cardp{\fnorm{\alpha_{i}}}{\fnorm{\ket{\Psi}}}\,,\label{eq:cardinalProbability}
\end{equation}
where every probability amplitude $\alpha_{i}\in F^{D}\left(k\right)$
so that both $\fnorm{\alpha_{i}}$ and $\fnorm{\ket{\Psi}}$ are within
the order range $S_{0}\left(k\right)$, and $\muC_{\Psi}\left(i\right)$
is called the cardinal probability of measuring $\ket{i}$. For example,
let $p=311$, $k=11$, and $D=2$. The permitted range is $S_{0}\left(11\right)=\{-5,\ldots,-1,0,1,\ldots,5\}$,
given the dimension $D=2$, the allowed probability amplitude coefficients
are $F^{2}\left(11\right)=\left\{ 0,\pm1,\pm\rmi,\left(\pm1\pm\rmi\right)\right\} $
(see Table~\ref{table_allowed}). Now the cardinal probabilities
of several representative one-qubit states are listed in Table~\ref{f11-proj.fig}.
\begin{table}
\begin{doublespace}
\noindent \centering{}\caption{\label{f11-proj.fig}Field norms and probabilities for one-qubit states
$\ket{\Psi}$ in $F^{2}\left(11\right)$.}
\begin{tabular}{cccccc}
\toprule 
$\ket{\Psi}$ & $\fnorm{\ip{0}{\Psi}}$ & $\fnorm{\ip{1}{\Psi}}$ & $\fnorm{\ket{\Psi}}$ & $\muC_{\Psi}\left(0\right)$ & $\muC_{\Psi}\left(1\right)$\tabularnewline
\midrule
$1\ket{0}$ & $1$ & $0$ & $1$ & $\cardp{1}{1}$ & $\cardp{0}{1}$\tabularnewline
$1\ket{0}+1\ket{1}$ & $1$ & $1$ & $2$ & $\cardp{1}{2}$ & $\cardp{1}{2}$\tabularnewline
$1\ket{0}+(1+\rmi)\ket{1}$ & $1$ & $2$ & $3$ & $\cardp{1}{3}$ & $\cardp{2}{3}$\tabularnewline
$(1-\rmi)\ket{0}+(1+\rmi)\ket{1}$ & $2$ & $2$ & $4$ & $\cardp{2}{4}$ & $\cardp{2}{4}$\tabularnewline
\bottomrule
\end{tabular}
\end{doublespace}
\end{table}

@@

Let's walk through the state in each iteration to make sure the algorithm
works. Because the probability amplitudes of $\ket{\overline{x}}$
are all the same for $\overline{x}\neq\overline{0}$, we can let $a_{l}$
be the probability amplitude of $\ket{\overline{0}}$, with $b_{l}$
the probability amplitude of each of the other possibilities, which
are all the same, after the operators $\Delta R$ is applied $l$
times. Beginning at $l=0$ with the information-less state, the normalization
scaled to integer values as usual, the state after $l$-th iteration
can be written as %
\begin{comment}
\todo{Verify the computation??}
\end{comment}
\begin{equation}
\begin{pmatrix}a_{l}\\
b_{l}\\
\vdots\\
b_{l}
\end{pmatrix}=\left(\Delta R\right)^{l}\begin{pmatrix}1\\
1\\
\vdots\\
1
\end{pmatrix}=\Delta R\begin{pmatrix}a_{l-1}\\
b_{l-1}\\
\vdots\\
b_{l-1}
\end{pmatrix}\,.
\end{equation}
We can solve the above iteration by the following recurrence relation
for the successive coefficients:
\begin{subequations}
\begin{align}
a_{0} & =1\,, & a_{l+1} & =\left(\frac{N}{2}-1\right)a_{l}+\left(N-1\right)b_{l}\,,\\
b_{0} & =1\,, & b_{l+1} & =\left(-1\right)a_{l}+\left(\frac{N}{2}-1\right)b_{l}\,.
\end{align}
\end{subequations}
We also know $\left|a_{j}\right|>\left|b_{j}\right|$, so we can estimate
an upper bound for the maximum cardinal probability as $\max\fnorm{a_{j}}\leq2\left(\frac{N}{2}\right)^{2j+1}$.
By applying Eq.~\eqref{eq:region} with $D=N=2^{n}$, we can estimate~$k$
using $k\geq8\left(\frac{N}{2}\right)^{2j+2}+1$. We can then pick
a prime $k$, and choose the $\pi\left(k\right)$-th prime in the
sequence represented by Table~\ref{pseq} guaranteeing that every
number we need for the computation is within the transitively ordered
range $F^{D}\left(k\right)$.

>>>>

\begin{table}[!t]
\begin{doublespace}
\noindent \centering{}\caption{\label{tab:teacher}Other courses I took which is relevant to this
dissertation, where IUB stands for Indiana University Bloomington
and NTU stands for National Taiwan University.}
%% ERT block 1 (before LyX tabular)
\renewcommand{\tabular}{\tabularx{\linewidth}}
\renewcommand{\endtabular}{\endtabularx} 
\begin{tabular}{M{Chou~(周謀鴻)}cM{MATH-M522}Y}
\toprule 
Instructor & School & Course & Relation with the dissertation\tabularnewline
\midrule
\midrule 
Tom Lewis & IUB & SLST-T501 & Sec.~\ref{subsec:Discrete-Deutsch-algorithm} is based on the term
paper of \emph{Academic Writing}.\tabularnewline
\midrule 
Michael\nolinebreak[3] A. Mandell & IUB & MATH-M522 & The textbook~\cite{Hatcher2001} of \emph{Topology II} is cited
in Chapters~\ref{chap:Introduction} and~\ref{chap:Conventional-Quantum-Theory}.\tabularnewline
\midrule 
Steven Myers & IUB & CSCI-B502 & The textbook~\cite{AroraBarak2009} of \emph{Computational Complexity}
is cited in Sec.~\ref{modalquantumcomputing}.\tabularnewline
\midrule 
Valery Lunts & IUB & MATH-M501 & The textbook~\cite{DummitFoote2004} of \emph{Survey of Algebra}
is cited in Secs.~\ref{sec:background}, \ref{discretequantumtheoryI},
and~\ref{discretequantumtheoryIIb}.\tabularnewline
\midrule 
Huah Chu\linebreak[3] (朱樺\textenglish[variant=american]{)} & NTU & 221~U3830\linebreak[3] 221~U3840 & The textbook~\cite{Artin1991} of \emph{Algebra (I)} and \emph{(II)}
is cited in Secs.~\ref{subsec:Two-dimensional-Hilbert-Space}, \ref{subsec:Cyclic-Properties-of},
\ref{subsec:Complexified-Finite-Fields}, and~\ref{discretequantumtheoryIIb}.\tabularnewline
\midrule 
Jin-Tzu Chen\linebreak[3] (陳金次) & NTU & 201~31300 & The textbook~\cite{GAMELIN2003} of \emph{Functions of a Complex Variable}
is cited in Sec.~\ref{subsec:Vector-Spaces}.\tabularnewline
\midrule
Mo-Hong\linebreak[3] Chou (周謀鴻) & NTU & 221~U4290 & The textbook~\cite{GolubVanLoan1996} of \emph{Introduction to Computational Linear Algebra}
is cited in Sec.~\ref{subsec:Finite-Precision-Extension-of}.\tabularnewline
\bottomrule
\end{tabular}% ERT block 2 (after LyX tabular)
\renewcommand{\tabular}{\ORIGtabular}
\renewcommand{\endtabular}{\ORIGendtabular} 
\end{doublespace}
\end{table}
Many people have done everything to make my double-major smooth. I
need to thank all of their supports, financially or providing some
experience, as listed in my Curriculum Vitae at the end of the dissertation.
Most importantly, Prof.\ Amr A. Sabry\ (\textarabic{عمرو صبري})
helped me deal with the rules, supervised my reading courses for writing
our papers, and financially support me as a research assistant and
associate. In the department of Mathematics, I need to thank the directors
of graduate study in Mathematics, especially Prof.\ Christopher Judge,
Prof.\ Matthias Weber, and Prof.\ Michael A.\ Mandell; and the
graduate services assistant, Kate Forrest. In the department of Computer
Science, I want to thank the directors of \PhD study in Computer
Science, especially Prof.\ Yuqing Melanie Wu (吴愈青) and Prof.\ \textturkish{Funda
Ergun}; the graduate student office; the director of AI/UI assignments,
Charles Pope; and the infrastructure and technology group (ITG). Particularly,
I don't know how much computational power I consumed to count the
states in Sec.~\ref{subsec:Maximal-entanglement}. This computational
power not only came from the Linux systems in Computer Science but
also came from the Big Red II administrated by University Information
Technology Services (UITS). Indiana University Libraries was also
extremely helpful during my dissertation research. Except for a stack
of books I checked out directly, while the books are not in their
collection, I occasionally requested them via the Interlibrary Loan
service or recommended IU libraries to purchase them.

@@

\begin{table}
\begin{doublespace}
\noindent \centering{}\caption{\label{tab:Possible-f}All Possible $f\colon\boolt\rightarrow\boolt$.}
\begin{tabular}{ccccc}
\toprule 
$x$ & $f_{1}\left(x\right)$ & $f_{2}\left(x\right)$ & $f_{3}\left(x\right)$ & $f_{4}\left(x\right)$\tabularnewline
\midrule
$\bfalse$ & $\bfalse$ & $\bfalse$ & $\btrue$ & $\btrue$\tabularnewline
$\btrue$ & $\bfalse$ & $\btrue$ & $\bfalse$ & $\btrue$\tabularnewline
\midrule 
constant or balanced? & constant & balanced & balanced & constant\tabularnewline
\bottomrule
\end{tabular}
\end{doublespace}
\end{table}
\begin{comment}
\todo{We typeset $U_{f}$ either directly or use macro \textbackslash uf,
but the definition of \textbackslash uf has a negative space between
$U$ and $f$ which is different from U\_\{f\}\ldots{} I need to understand
whether the negative space is necessary or not, or whether the negative
space has any semantic meaning\ldots{} }
\end{comment}
Although having no realistic application, the Deutsch algorithm is
the first quantum algorithm which outperforms any possible classical
algorithm for the Deutsch problem \cite{Deutsch1985,544199,Mermin2007}.
The Deutsch problem is to decide whether a function $f\colon\boolt\rightarrow\boolt$
is constant or balanced. As listed in Table~\ref{tab:Possible-f},
we have only $4$ different $f$: $2$ of them are constant while
another $2$ are balanced. Similar to our $\usat$ algorithm in Sec.~\ref{modalquantumcomputing},
we start by representing $f$ as a Deutsch black box $U_{f}$ in the
middle of the quantum circuit, Figure~\ref{fig:Quantum-Circuit-Deutsch}.
To explain why this circuit solves the Deutsch problem, we then compute
the state in each step explicitly and express them in the Dirac bracket
notation and its matrix representation in the computational basis
$\left\{ \ket{00},\ket{01},\ket{10},\ket{11}\right\} $.
\begin{figure}[!b]
\noindent \centering{}
\[
\begin{array}{c}
\xyR{.9em}\xyC{.6em}\entrymodifiers={@*=<0em>}\xymatrix{ & \ar@{.}[ddd] &  & \ar@{.}[ddd] &  & \ar@{.}[ddd] &  & \ar@{.}[ddd]\\
\lstick{\ket{1}} & \qw & \gate{H} & \qw & \multigate{1}{\uf} & \qw & \gate{H^{\dagger}} & \qw & \multimeasureD{1}{\text{measure}}\\
\lstick{\ket{0}} & \qw & \gate{H} & \qw & \ghost{\uf} & \qw & \gate{H^{\dagger}} & \qw & \ghost{\text{measure}}\\
 & \push{\ket{\Phi_{1}}} &  & \push{\ket{\Phi_{2}}} &  & \push{\ket{\Phi_{3}}} &  & \push{\ket{\Phi_{4}}}
}
\end{array}
\]
\caption{\label{fig:Quantum-Circuit-Deutsch}Quantum Circuit for the Deutsch
Algorithm.}
\end{figure}

@@

As an example, consider the field $\ff{23}$. Looking at the squares
of the numbers $\ff{23}=\{0,\ldots,22\}$ modulo 23, we find the $2$-centered
uninterrupted sequence $S_{2}\left(5\right)=\{0,1,2,3,4\}$, followed
by $5$, which is both the smallest quadratic non-residue and the
size of the uninterrupted sequence of quadratic residues (including
$0$) of interest. In particular, it is possible to construct a total
order for the elements $S_{0}\left(5\right)=\{-2,-1,0,1,2\}$ in the
fields $\ff{23}$, $\ff{71}$, $\ff{311}$, etc., but not in the smaller
fields $\ff{3}$ and $\ff{7}$.

@@

Although division is not an allowed operation for the elements in
an ordered region, following the standard procedure to define a conventional
fraction as a pair of integers \cite{Artin1991,DummitFoote2004,hottbook2013,Wolfram2016},
we could define a \emph{cardinal probability} as a pair of order-region
elements as well:
\begin{equation}
\muC_{\Psi}\left(i\right)=\cardp{\fnorm{\ip{i}{\Psi}}}{\fnorm{\ket{\Psi}}}=\cardp{\fnorm{\alpha_{i}}}{\fnorm{\ket{\Psi}}}\,,\label{eq:cardinalProbability}
\end{equation}
where every probability amplitude $\alpha_{i}\in F^{D}\left(k\right)$
so that both $\fnorm{\alpha_{i}}$ and $\fnorm{\ket{\Psi}}$ are within
the order range $S_{0}\left(k\right)$, and $\muC_{\Psi}\left(i\right)$
is called the cardinal probability of measuring $\ket{i}$. For example,
let $p=311$, $k=11$, and $D=2$. The permitted range is $S_{0}\left(11\right)=\{-5,\ldots,-1,0,1,\ldots,5\}$,
given the dimension $D=2$, the allowed probability amplitude coefficients
are $F^{2}\left(11\right)=\{0,\pm1,\pm\rmi,\left(\pm1\pm\rmi\right)\}$
(see Table~\ref{table_allowed}). Now the cardinal probabilities
of several representative one-qubit states are listed in Table~\ref{f11-proj.fig}.
\begin{table}
\begin{doublespace}
\noindent \centering{}\caption{\label{f11-proj.fig}Field norms and probabilities for one-qubit states
$\ket{\Psi}$ in $F^{2}\left(11\right)$.}
\begin{tabular}{cccccc}
\toprule 
$\ket{\Psi}$ & $\fnorm{\ip{0}{\Psi}}$ & $\fnorm{\ip{1}{\Psi}}$ & $\fnorm{\ket{\Psi}}$ & $\muC_{\Psi}\left(0\right)$ & $\muC_{\Psi}\left(1\right)$\tabularnewline
\midrule
$1\ket{0}$ & $1$ & $0$ & $1$ & $\cardp{1}{1}$ & $\cardp{0}{1}$\tabularnewline
$1\ket{0}+1\ket{1}$ & $1$ & $1$ & $2$ & $\cardp{1}{2}$ & $\cardp{1}{2}$\tabularnewline
$1\ket{0}+(1+\rmi)\ket{1}$ & $1$ & $2$ & $3$ & $\cardp{1}{3}$ & $\cardp{2}{3}$\tabularnewline
$(1-\rmi)\ket{0}+(1+\rmi)\ket{1}$ & $2$ & $2$ & $4$ & $\cardp{2}{4}$ & $\cardp{2}{4}$\tabularnewline
\bottomrule
\end{tabular}
\end{doublespace}
\end{table}

@@

Let's walk through the state in each iteration to make sure the algorithm
works. Because the probability amplitudes of $\ket{\overline{x}}$
are all the same for $\overline{x}\neq\overline{0}$, we can let $a_{l}$
be the probability amplitude of $\ket{\overline{0}}$, with $b_{l}$
the probability amplitude of each of the other possibilities, which
are all the same, after the operators $\Delta R$ is applied $l$
times. Beginning at $l=0$ with the information-less state and the
normalization scaled to integer values as usual, the state after $l$-th
iteration can be written as %
\begin{comment}
\todo{Verify the computation??}
\end{comment}
\begin{equation}
\begin{pmatrix}a_{l}\\
b_{l}\\
\vdots\\
b_{l}
\end{pmatrix}=\left(\Delta R\right)^{l}\begin{pmatrix}1\\
1\\
\vdots\\
1
\end{pmatrix}=\Delta R\begin{pmatrix}a_{l-1}\\
b_{l-1}\\
\vdots\\
b_{l-1}
\end{pmatrix}\,.
\end{equation}
We can solve the above iteration by the following recurrence relation
for the successive coefficients:
\begin{subequations}
\begin{align}
a_{0} & =1\,, & a_{l+1} & =\left(\frac{N}{2}-1\right)a_{l}+\left(N-1\right)b_{l}\,,\\
b_{0} & =1\,, & b_{l+1} & =\left(-1\right)a_{l}+\left(\frac{N}{2}-1\right)b_{l}\,.
\end{align}
\end{subequations}
We also know $\left|a_{j}\right|>\left|b_{j}\right|$, so we can estimate
an upper bound for the maximum cardinal probability as $\max\fnorm{a_{j}}\leq2\left(\frac{N}{2}\right)^{2j+1}$.
By applying Eq.~\eqref{eq:region} with $D=N=2^{n}$, we can estimate~$k$
using $k\geq8\left(\frac{N}{2}\right)^{2j+2}+1$. We can then pick
a prime $k$, and choose the $\pi\left(k\right)$-th prime in the
sequence represented by Table~\ref{pseq} guaranteeing that every
number we need for the computation is within the transitively ordered
range $F^{D}\left(k\right)$.
